Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study

### 2024-12-09 paper/main.tex
modifications

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset\footnote{For reference of the complete dataset:\\ 
	\url{https://github.com/HENERALPEPITO/ML-miniproject/tree/main/datasets}}, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases). To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, and temperature. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends.

>>>>

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset\footnote{For reference of the complete dataset:\\ 
	\url{https://github.com/HENERALPEPITO/ML-miniproject/tree/main/datasets}}, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases). To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, temperature, and cases. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends.
